---
title: "STAT 118: Homework N"
subtitle: 'Multiple Regression'
author: "YOUR NAME HERE"
format:
  html: 
    toc: true
    code-overflow: wrap
    code-fold: true
    embed-resources: true
---

```{r message=FALSE, warning=FALSE}
#LOAD PACKAGES 
library(tidyverse)
library(palmerpenguins)

#LOAD DATA
data('penguins')
```


# 1. 
Create a scatterplot of body mass (x variable) vs. flipper length (y variable). Include a linear line of best fit on top of your graph. 

# 2.
Find a linear model using `lm()` which predicts flipper length based on the penguin's body mass -- call this model `fit1`. Interpret the slope coefficient. 

# 3.
Suppose we are interested in the predicting flipper length based on the sex (male or female) of the penguin. Create a side-by-side boxplot -- there should be a boxplot for the length of flippers of female penguins next to a boxplot for the length of flippers of male penguins. Make sure your axes are clearly labeled. 

```{r}
# To make a side by side boxplot
# dataset %>% 
# ggplot(aes(x=categorical variable, y = quantiative variable))+
# geom_boxplot()

```


# 4. 
Find a linear model using `lm()` which predicts flipper length based on the penguin's species -- called this model `fit2`.  


# 5.
Using `fit2`, what species was used as the "base level"?

# 6.
Using `fit2`, what do you predict the flipper length to be for each of the three species (on average)? 

# 7.
Using `fit2`, check out the p-values for each of the slope coefficients. If the p-value is less than 0.05, we say that term is significant and that variable has a significant impact on flipper length. If the p-value is 0.05, we say the term is not significant and that variable does not have a significant impact on flipper length. Are each of your slope coefficients significant or not? 

# 8.
Find a linear model using `lm()` which predicts flipper length based on the penguin's body mass AND the penguin's species. Do not include an interaction term. Call this model `fit3`

# 9.
Using `fit3`, check out the p-values for each of the slope coefficients. If the p-value is less than 0.05, we say that term is significant and that variable has a significant impact on flipper length. If the p-value is 0.05, we say the term is not significant and that variable does not have a significant impact on flipper length. Are each of your slope coefficients significant or not? 

# 10.
Suppose we have a Gentoo Penguin with body mass of 4500g. Using the model `fit3`, what would you predict that penguin's flipper length to be? 

# 11.
Create a scatterplot of body mass (x variable) vs. flipper length (y variable). Use color to represent each of the 3 different species of penguins. Use `geom_parallel_slopes()` to display the lines of best fit for each penguin species for model `fit3`. 

# 12.
Find a linear model using `lm()` which predicts flipper length based on the penguin's body mass AND the penguin's species. Please include an interaction term. Call this model `fit4`. 

# 13.
Using `fit4`, check out the p-values for each of the slope coefficients. If the p-value is less than 0.05, we say that term is significant and that variable has a significant impact on flipper length. If the p-value is 0.05, we say the term is not significant and that variable does not have a significant impact on flipper length. Are each of your slope coefficients significant or not? 

# 14. 
Suppose we have a Gentoo Penguin with body mass of 4500g. Using the model `fit4`, what would you predict that penguin's body weight to be? 

# 15.
Create a scatterplot of body mass (x variable) vs. flipper length (y variable). Use color to represent each of the 3 different species of penguins. Use `geom_smooth` to display the lines of best fit for each penguin species from model `fit4`.

# 16.
Using `fit4`, which species would an increase in body weight have the most effect on flipper length? 