---
title: "MATH 118: Homework I"
subtitle: 'custom colors, labels'
author: " "
output:
  html_document:
    code_folding: hide
---

```{r message=FALSE, warning=FALSE}
#LOAD PACKAGES 
library(tidyverse)
library(RColorBrewer)
#LOAD DATA
library(gapminder)
data("gapminder")
```

1. Choose two of the Color Brewer palettes and visualize them using the `colorBlindness` package. Comment on whether you see any concerns about not being able to differentiate between the colors. In your opinion, is one of the palettes you choose better than the other? 

2. Consider the graph below. Add a label on each point which displays the corresponding country name. I'm not picky on which type of label you use, but I encourage you to pick something that makes it easy for your audience to read your labels. 

```{r}
gapminder %>% 
  filter(year=="2007") %>% 
  filter(continent == "Asia") %>% 
  ggplot(aes(gdpPercap, lifeExp))+
  geom_point()+
  scale_x_log10() +
  xlab("GDP per Capita")+
  ylab("Life Expectancy") +
  theme_minimal()+
  ggtitle("Countries in Asia in 2007") 
```

3. Consider the graph below. Choose three countries -- add a label on three points which displays the corresponding country names. I'm not picky on which type of label you use, but I encourage you to pick something that makes it easy for your audience to read your labels.  

```{r}
gapminder %>% 
  filter(year=="2007") %>% 
  ggplot(aes(gdpPercap, lifeExp))+
  geom_point(aes(color = continent))+
  scale_x_log10() +
  xlab("GDP per Capita")+
  ylab("Life Expectancy") +
  theme_minimal()+
  ggtitle("Countries of the World in 2007")
```

4. Consider the graph below. Recolor the graph using an appropriate color palette from the `RColorBrewer` package. 

```{r}
gapminder %>% 
  filter(year=="2007") %>% 
  ggplot(aes(gdpPercap, lifeExp))+
  geom_point(aes(color = continent))+
  scale_x_log10() +
  xlab("GDP per Capita")+
  ylab("Life Expectancy") +
  theme_minimal()+
  ggtitle("Countries of the World in 2007")
```

5. Consider the graph below. Recolor the graph using five custom colors of your choosing. You should check that your five color choices are color blind friendly using the `colorBlindness` package. 

```{r}
gapminder %>% 
  filter(year=="2007") %>% 
  ggplot(aes(gdpPercap, lifeExp))+
  geom_point(aes(color = continent))+
  scale_x_log10() +
  xlab("GDP per Capita")+
  ylab("Life Expectancy") +
  theme_minimal()+
  ggtitle("Countries of the World in 2007")
```

6. Consider the variables below. Which types of color pattern (sequential, diverging, or qualitative) do you think would work best? There are images on the homework page that might help you with your choice. 

(a) Unemployment Rates (ie. 3.4%)

(b) Opinion Scale (Strongly Disagree, Disagree, Neutral, Agree, Strongly Agree)

(c) Countries (India, USA, or others)


