---
title: 'MATH 118: Notes D'
author: ' '
subtitle: pretty tables with xtable + a little ggplot
output:
  pdf_document: default
  html_document:
    code_folding: hide
  word_document: default
---

```{r message=FALSE, warning=FALSE}
#LOAD PACKAGES 
library(tidyverse)
```

Let's consider our table from last class: 

```{r message=FALSE, warning=FALSE}
#LOAD DATA 
library(palmerpenguins)
data(penguins)

#CLEAN UP DATA
penguins <- penguins %>%
  drop_na()
#sometimes this is appropriate. It's questionable here... 
```

```{r}
penguins %>%
  group_by(species) %>%
  summarise(average_bill_lenth = mean(bill_length_mm), 
            average_bill_depth = mean(bill_depth_mm))
```

When we knit this up it looks like of ugly... 

# Using `kable` to get pretty tables

```{r message=FALSE, warning=FALSE}
library(kableExtra)
```


```{r}
penguins %>%
  group_by(species) %>%
  summarise(average_bill_length = mean(bill_length_mm), 
            average_bill_depth = mean(bill_depth_mm)) %>% 
  kbl()

#OR 

table1 <- penguins %>%
  group_by(species) %>%
  summarise(average_bill_length = mean(bill_length_mm), 
            average_bill_depth = mean(bill_depth_mm))

kbl(table1)
```

Note that kable will work if you knit to .html (like we do in this class), but also if you choose to knit to Word or PDF (note you need to install some things to knit to PDF). 

# Options in kable

We customize the content so it's displaying the information more clearly. 


```{r}
table1 %>%
  kbl(col.names = c("Species", "Average Bill Length", "Average Bill Depth"), 
    caption = "Average Bill Characteristics by Species", 
    digits = 2)
```

Better...  

# pretty styling 

```{r}
table1 %>%
  kbl(col.names = c("Species", "Average Bill Length", "Average Bill Depth"), 
    caption = "Average Bill Characteristics by Species", 
    digits = 2) %>%
  kable_styling()
```

Many options for customizing the look of the tables -- more here: [https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html](https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html)

Let's try one... 

Let's make each row's color correspond to 

```{r}
table1 %>%
  kbl(col.names = c("Species", "Average Bill Length", "Average Bill Depth"), 
    caption = "Average Bill Characteristics by Species", 
    digits = 2) %>%
  kable_paper() %>%
  column_spec(1, bold=T) %>%
  row_spec(2, color = "#c85bcc") %>%
  row_spec(3, color = "#067176") %>%
  row_spec(1, color = "#ff7501")
```


RStudio hosts a table contest every year!

- Here is a link to this year's contest [https://www.rstudio.com/blog/rstudio-table-contest-2022/](https://www.rstudio.com/blog/rstudio-table-contest-2022/)
- Here is a link to previous year's entries and winners to explore what is possible! [https://community.rstudio.com/c/table-gallery/64](https://community.rstudio.com/c/table-gallery/64)

# Introduction to ggplot

```{r}
table1 %>% 
ggplot(aes(x = species, y = average_bill_length)) +
geom_bar(stat = "identity") 
```



```{r}
table1 %>% 
ggplot(aes(x = species, y = average_bill_length, fill=species)) +
geom_bar(stat = "identity") +
scale_fill_manual(values = c("#ff7501","#c85bcc", "#067176")) + 
ylab("Average Bill Length") + 
theme_minimal() + 
theme(legend.position = "none") 
```
```{r}
penguins %>% 
  ggplot(aes(x=flipper_length_mm, y=body_mass_g)) +
  geom_point() 
```

```{r}
penguins %>% 
  ggplot(aes(x=flipper_length_mm, y=body_mass_g, color=species)) +
  geom_point() +
  scale_color_manual(values = c("#ff7501","#c85bcc", "#067176")) + 
  xlab("Flipper Length (in mm)")+
  ylab("Body Mass (in g)") + 
  theme_minimal()
```
