---
title: "MATH 118: Homework F"
subtitle: 'Joining tables with dplyr'
author: " "
output:
  html_document:
    code_folding: hide
---

```{r message=FALSE, warning=FALSE}
#LOAD PACKAGES 
library(tidyverse)

#Load gapminder data
library(gapminder)
data(gapminder)
```

1. Use your brain and skills to figure out what the code below is doing. Add a sentence discribing what this does. 

```{r}
country_continent <- gapminder %>% 
  select(country, continent) %>% 
  distinct()
```

2. What columns do `country_continent` and `co2` have in common? (*This is your key*)

3. What columns does `country_continent` have that `co2` doesn't? 

4. What columns does `co2` have that `country_continent` doesn't? 

5. Create a new table called `co2_joined`, which includes all columns from `co2` in addition to the column `continent`. To start, use `inner_join()`. Make a note of how many rows you have in the new table, and compare it with the original tables.

```{r}
co2_joined <- co2 %>% 
  left_join(country_continent, by="country")
```

6. Create a new table called `co2_joined_left`, which includes all columns from `co2` in addition to the column `continent` but this time use `left_join()` instead of `inner_join()`. Make a note of how many rows you have in the new table, and compare it with the original tables.

```{r}
co2_joined_left <- co2 %>% 
  left_join(country_continent, by="country")
```


7. Download the `co2.csv` file from Canvas. Import the dataset into this assignment in a dataframe called `co2`. 

```{r}
co2 <- read.csv("data/co2.csv")
```

8. What columns do `gapminder` and `co2` have in common? 

9. What columns does `gapminder` have that `co2` doesn't? 

10. What columns does `co2` have that `gapminder` doesn't? 

11. Create a new table called `gapminder_joined`, which includes all rows from both tables joined together by their common variable keys (use `inner_join()`). Make a note of how many rows you have in the new table, and compare it with the original tables.

```{r}
gapminder_joined <- gapminder %>% 
    inner_join(co2, by=c("country", "year"))
```

12.  Use the `anti_join()` function to identify which rows (if anyt) in the `gapminder` dataset do NOT have a match in out `co2` dataset. 

```{r}
gapminder %>% 
    anti_join(co2, by=c("country", "year"))
```

13. Use the `anti_join()` function to identify which rows (if anyt) in the `co2` dataset do NOT have a match in out `gapminder` dataset.

```{r}
co2 %>% 
    anti_join(gapminder, by=c("country", "year"))
```


15. Create a new column in `gapminder_joined` called `ratio` which indicates the ratio of `co2_emissions_pc` divided by `gdpPercap`. 

```{r}
gapminder_joined <- gapminder_joined %>% 
  mutate(ratio = co2_emissions_pc /gdpPercap )
```


14. Use `gapminder_joined` to create a scatterplot of  `gdpPercap` vs. `co2_emissions_pc`. 

```{r}
gapminder_joined %>% 
  filter(year == "2007") %>% 
  ggplot(aes(x=gdpPercap, y=co2_emissions_pc)) + 
  geom_point() 
```



