---
title: "STAT 118: Homework P"
subtitle: 'Webscraping Text with `rvest`'
author: "YOUR NAME HERE"
format:
  html: 
    toc: true
    code-overflow: wrap
    code-fold: true
    embed-resources: true
---

```{r}
#make sure the package is installed on your computer or this won't run! 
library(tidyverse)
```


1. The following problems will involve scraping data from [https://www.scrapethissite.com/pages/simple/](https://www.scrapethissite.com/pages/simple/). 


a) scrape the names of all the countries *Hint: use .country-name*

```{r}

```


b) Scrape the names of each country's capital. *Hint: use .country-capital* 

```{r}

```

c) Scrape the population of each country. No hints this time. 

```{r}

```

d) Scrape the area of each country. No hints this time. 

```{r}

```

e) Combine the information you've scraped in a) - d) and combine it together into one dataframe called `countries`. Give each of the columns appropriate names.

```{r}

```

f) Create a new column called `Density` in the dataframe `countries` which contains the population density of each country. *Hint: Population Density is calculated as Population divided by area*

```{r}

```

g) Create a barplot which displays the top 10 countries with the highest population density. Be sure you axes are appropriately labeled. 

```{r}

```


2. Scrape a table of your choice from Wikipedia. Remember you need to use `html_table` instead of `html_text`. Try to pick a simple table with one header, unless you are feeling up for a challenge.  Be sure to print out the table for Emily and Violet to see. 

```{r}

```

